SunPy - Python for Solar Physics

### 2014-08-27 2-Data_Types.tex

The core of SunPy is a set of data structures that are specifically designed for the
three primary varieties of solar physics data: images, time series, and
spectra. These core data types are supported by SunPy's classes:
\texttt{Map} (2D spatial data), \texttt{LightCurve} (1D temporal series),
and \texttt{Spectrum} and \texttt{Spectrogram} (1D and 2D spectra).

>>>>

The core of SunPy is a set of data structures that are specifically
designed for the three primary varieties of solar physics data:
images, time series, and spectra. These core data types are supported
by the SunPy classes: \texttt{Map} (2D spatial data),
\texttt{LightCurve} (1D temporal series), and \texttt{Spectrum} and
\texttt{Spectrogram} (1D and 2D spectra).  The purpose of these
classes is to provide the same core data type to the SunPy user
regardless of the differences in source data.  For example, if two
different instruments use different time formats to describe the
observation time of their images, the corresponding SunPy \texttt{Map}
object for each of them expresses the observation time in the same
way.  This simplifies the workflow for the user when handling data
from multiple sources.
